% Appendix: AI Tools Usage Disclosure
% AI 工具使用声明（2026 规则必读）
% 【重要警告 - 2026 年规则严格！】
%
% 填写要点：逐条列出工具、对应章节/任务与具体用途；避免空泛描述。
%
% ▶ 关键原则：
%   "所有数学推导、模型设计、创新点必须是原创"
%   "AI 仅作为效率工具，不替代核心思考"

\section*{Use of AI}
\addcontentsline{toc}{section}{Use of AI}
\label{appendix:ai}

% 【说明】根据 COMAP 2026 官方要求，必须提交 AI 使用声明
In accordance with the COMAP 2026 rules, we hereby disclose all uses of artificial intelligence (AI) tools during the preparation of this paper.

% AI 使用详细记录表

% 【重要】使用 tabularx 让 Description 列自动换行，避免手动断行
\begin{table}[H]
    \centering
    \caption{Detailed AI Usage Log (Per COMAP 2026 Requirements)}
    \label{tab:ai_disclosure}
    \begin{tabularx}{\textwidth}{l l X}
        \toprule
        \textbf{AI Tool} & \textbf{Section / Task} & \textbf{Specific Usage Description} \\
        \midrule
        % --- 示例条目（请根据实际情况修改）---
        ChatGPT-4o & Abstract & 
        Used for polishing English grammar and improving sentence fluency. All technical content was written by team members. \\
        \addlinespace[0.5em]
        
        GitHub Copilot & Section 5 (Code) & 
        Assisted in writing Python scripts for data preprocessing and visualization. All algorithmic logic was designed by the team. \\
        \addlinespace[0.5em]
        
        Claude 3.5 Sonnet & Section 4 (Model) & 
        Helped organize mathematical notations and check LaTeX formatting. Model derivations are original work. \\
        \addlinespace[0.5em]
        
        Gemini 1.5 Pro & Data Analysis & 
        Used to generate initial exploratory plots from the dataset. Final figures were recreated by our team with custom styling. \\
        \addlinespace[0.5em]
        
        DeepL Translator & Throughout & 
        Assisted in translating technical terms between Chinese and English. All final text was reviewed and revised by team members. \\
        \bottomrule
    \end{tabularx}
\end{table}

% 原创性声明
\subsection*{Declaration of Originality}
\label{subsec:originality}

% 【模板文本 - 可根据需要修改】
We, the members of Team \#2617892, hereby declare that:

\begin{enumerate}[label=\arabic*., itemsep=0.5em]
    \item \textbf{Core Intellectual Work:} All problem analysis, mathematical modeling, algorithm design, and innovative contributions presented in this paper are the \textbf{original work} of our team members.
    
    \item \textbf{AI as Auxiliary Tool:} AI tools were used solely as auxiliary aids for improving language quality, formatting documents, and accelerating repetitive coding tasks. \textbf{No AI was used to generate core mathematical derivations or modeling ideas.}
    
    \item \textbf{Human Oversight:} All AI-generated content was carefully reviewed, verified, and often substantially modified by team members before inclusion in the final paper.
    
    \item \textbf{Code Verification:} All code assisted by AI tools was independently tested and validated by our team to ensure correctness and reproducibility.
    
    \item \textbf{Academic Integrity:} We have read and understood the COMAP 2026 rules regarding AI usage and academic integrity. We affirm that this disclosure is complete and accurate.
\end{enumerate}

% 补充说明（可选）
\subsection*{Additional Notes}
\label{subsec:ai_notes}

% 【提示】如有特殊情况，在此说明
\begin{itemize}[itemsep=0.3em]
    \item The raw conversation logs with AI tools are available upon request for verification purposes.
    \item Total estimated AI-assisted work: approximately 15\% of the paper content (primarily language polishing and code formatting).
    \item All figures in this paper were generated using Python (Matplotlib/Seaborn) with code written or reviewed by team members.
\end{itemize}

% 签名区域（可选）
\vspace{1cm}
\noindent\rule{\textwidth}{0.4pt}

\noindent
\textbf{Team \#2617892}\\
Date: \today

% 【注意】实际提交时，日期应为比赛截止日期
% Date: February 10, 2026
