% Section 10: Policy Recommendations
% 政策建议：可操作性和现实意义

\section{Policy Recommendations}
\label{sec:policy}

% 【E题O奖核心要求】政策建议必须独立成章，具有可操作性

%=== 10.1 政策建议框架 ===
\subsection{Recommendation Framework}
\label{subsec:policy_framework}

Based on our quantitative analysis, we provide tiered, stakeholder-specific recommendations designed for actionability. Our recommendations follow the \textbf{SMART+A} framework:

\begin{itemize}[itemsep=0.2em]
    \item \textbf{S}pecific: Clear, unambiguous actions
    \item \textbf{M}easurable: Quantifiable targets where possible
    \item \textbf{A}chievable: Realistic given resource constraints
    \item \textbf{R}elevant: Directly addressing sustainability objectives
    \item \textbf{T}ime-bound: With explicit implementation timelines
    \item \textbf{+A}daptive: Built-in review and adjustment mechanisms
\end{itemize}

%=== 10.2 分层政策建议 ===
\subsection{Tiered Recommendations}
\label{subsec:tiered_recommendations}

\begin{quote}
\textbf{POLICY MEMORANDUM}

\textbf{To:} \TODO{Target decision-maker(s), e.g., Minister of Environment, Regional Planning Authority}

\textbf{From:} Team \#2617892

\textbf{Re:} Evidence-Based Sustainability Policy Recommendations for \TODO{Problem E Topic}

\textbf{Date:} \today

\vspace{1em}

\noindent\rule{\textwidth}{0.5pt}

\vspace{0.5em}
\textbf{Executive Summary:} Our analysis indicates that \TODO{Scenario S3 / recommended approach} offers the optimal balance of environmental protection, economic viability, and social equity. Below we provide actionable recommendations organized by implementation timeline.
\end{quote}

\subsubsection{Priority A: Immediate Actions (0--2 Years)}

\begin{enumerate}[itemsep=0.4em]
    \item \textbf{Establish Monitoring and Baseline Assessment}
    
    \textit{Action:} Deploy comprehensive monitoring systems for key sustainability indicators.
    
    \textit{Target:} Achieve \TODO{X\%} coverage of \TODO{target area/sector} within \TODO{timeframe}.
    
    \textit{Investment:} Approximately \TODO{\$X million} for infrastructure and personnel.
    
    \textit{Rationale:} Data-driven adaptive management requires robust baseline measurement.
    
    \item \textbf{Quick-Win Interventions}
    
    \textit{Action:} Implement low-cost, high-impact measures identified in our sensitivity analysis.
    
    \textit{Examples:} \TODO{e.g., Energy efficiency retrofits, waste reduction programs, public awareness campaigns}
    
    \textit{Expected Impact:} \TODO{X\% improvement in indicator Y within Z years}.
    
    \item \textbf{Stakeholder Engagement Platform}
    
    \textit{Action:} Create formal mechanisms for multi-stakeholder dialogue and co-management.
    
    \textit{Rationale:} Our analysis shows that stakeholder buy-in significantly affects implementation success.
\end{enumerate}

\subsubsection{Priority B: Medium-Term Investments (3--5 Years)}

\begin{enumerate}[itemsep=0.4em]
    \item \textbf{Infrastructure Transformation}
    
    \textit{Action:} Invest in \TODO{e.g., renewable energy infrastructure, sustainable transportation, green building standards}.
    
    \textit{Target:} \TODO{Specific quantitative target, e.g., 50\% renewable energy share by 2030}.
    
    \textit{Investment:} \TODO{\$X billion} over \TODO{Y years}, with expected ROI of \TODO{Z\%}.
    
    \item \textbf{Regulatory Framework Enhancement}
    
    \textit{Action:} Strengthen regulations for \TODO{target pollutant/activity} with clear enforcement mechanisms.
    
    \textit{Instruments:} Consider \TODO{e.g., carbon pricing, tradable permits, performance standards}.
    
    \item \textbf{Capacity Building}
    
    \textit{Action:} Invest in human capital through \TODO{e.g., training programs, technology transfer, institutional development}.
    
    \textit{Target:} Train \TODO{X} professionals in \TODO{relevant skills} by \TODO{year}.
\end{enumerate}

\subsubsection{Priority C: Long-Term Transformation (6--15 Years)}

\begin{enumerate}[itemsep=0.4em]
    \item \textbf{Systemic Transition}
    
    \textit{Action:} Pursue fundamental transformation of \TODO{e.g., energy system, agricultural practices, urban form}.
    
    \textit{Vision:} Achieve \TODO{long-term sustainability goal, e.g., net-zero emissions, circular economy}.
    
    \item \textbf{Resilience Building}
    
    \textit{Action:} Invest in adaptive capacity for \TODO{climate change impacts, resource scarcity, other long-term risks}.
    
    \item \textbf{International Cooperation}
    
    \textit{Action:} Engage in \TODO{e.g., technology sharing, coordinated policy, transboundary management} with neighboring jurisdictions.
\end{enumerate}

%=== 10.3 实施路线图 ===
\subsection{Implementation Roadmap}
\label{subsec:roadmap}

\begin{figure}[H]
    \centering
    \fbox{\parbox[c][0.25\textheight][c]{0.95\textwidth}{
        \centering
        \textbf{Implementation Roadmap Timeline}
        \par\vspace{0.5em}
        \small \TODO{Gantt chart or timeline diagram showing:
        \begin{itemize}
            \item Phase 1 (Years 0-2): Monitoring setup, quick wins, stakeholder platform
            \item Phase 2 (Years 3-5): Infrastructure investment, regulatory reform, capacity building
            \item Phase 3 (Years 6-15): Systemic transition, resilience building, international cooperation
            \item Key milestones and decision points
            \item Review and adaptation cycles
        \end{itemize}}
    }}
    \caption{Implementation roadmap for recommended sustainability transition.}
    \label{fig:roadmap}
\end{figure}

%=== 10.4 适应性管理机制 ===
\subsection{Adaptive Management Mechanism}
\label{subsec:adaptive}

Given the uncertainty inherent in long-term sustainability planning, we recommend an \textbf{adaptive management cycle}:

\begin{enumerate}[itemsep=0.3em]
    \item \textbf{Monitor:} Continuously track indicator performance against targets.
    
    \item \textbf{Evaluate:} Conduct periodic (e.g., 3-year) comprehensive reviews using updated data and models.
    
    \item \textbf{Learn:} Identify what is working, what is not, and why.
    
    \item \textbf{Adjust:} Modify policies, targets, and investments based on evidence.
    
    \item \textbf{Communicate:} Transparently report progress to stakeholders.
\end{enumerate}

\TODO{Specify trigger conditions for major policy adjustments, e.g., ``If environmental indicator falls below X, escalate intervention to Aggressive Transition pathway.''}

%=== 10.5 风险与缓解 ===
\subsection{Risks and Mitigation}
\label{subsec:risks}

\begin{table}[H]
    \centering
    \caption{Key Implementation Risks and Mitigation Strategies}
    \label{tab:risks}
    \begin{tabularx}{\textwidth}{l X X}
        \toprule
        \textbf{Risk} & \textbf{Impact} & \textbf{Mitigation} \\
        \midrule
        Political turnover & Policy discontinuity & Build cross-party consensus; embed in long-term legislation \\
        Funding shortfall & Delayed implementation & Diversify funding sources; prioritize high-ROI interventions \\
        Stakeholder resistance & Implementation failure & Early engagement; benefit-sharing mechanisms \\
        Climate shocks & Derailed progress & Build resilience buffers; maintain adaptive capacity \\
        Technology lock-in & Suboptimal path & Maintain technology neutrality; periodic review \\
        \bottomrule
    \end{tabularx}
\end{table}
