% 00_abstract.tex - Summary Sheet (摘要页)
% ICM Problem F - Policy Science

\begin{abstract}

% 【写作指导】F题摘要需突出：政策问题、建模方法、政策方案、评估结果、实施建议
% 篇幅控制在250-300词，结构清晰

% 第一段：政策背景与问题
Addressing the complex policy challenge of \textbf{\TODO{specific policy topic, e.g., resource allocation, social intervention, regulatory design}}, we develop an integrated modeling framework that bridges \textbf{rigorous quantitative analysis} with \textbf{actionable policy recommendations}. Our approach recognizes that effective policy design requires understanding both the \textit{mechanisms} through which interventions operate and the \textit{systemic impacts} they generate across diverse stakeholder groups.

% 第二段：建模方法
\noindent\textbf{Mechanism Modeling.}
We construct a \TODO{e.g., system dynamics / agent-based / game-theoretic} model to capture the causal pathways linking policy inputs to societal outcomes. The model incorporates \TODO{key mechanisms, e.g., behavioral responses, market dynamics, institutional constraints}, enabling scenario analysis across a range of policy intensities.

% 第三段：政策优化
\noindent\textbf{Policy Optimization.}
Building on the mechanism model, we formulate a \TODO{e.g., multi-objective optimization / robust decision-making} framework that balances competing objectives: \TODO{e.g., efficiency, equity, sustainability}. Our solution algorithm identifies Pareto-optimal policy portfolios that decision-makers can adapt to local priorities.

% 第四段：核心结果
\noindent\textbf{Key Findings.}
Scenario analysis reveals that \TODO{key policy insight, e.g., ``early intervention yields 2.3x returns compared to delayed action''}. Sensitivity testing confirms that recommendations remain robust under \TODO{uncertainty conditions}. We further analyze \textbf{spillover effects} and \textbf{long-term system stability} to ensure policy sustainability.

% 第五段：政策建议
\noindent\textbf{Policy Recommendations.}
We provide tiered, actionable recommendations in an attached \textbf{Policy Memorandum}, addressing implementation feasibility, resource requirements, and risk mitigation strategies for \TODO{target decision-maker}.

\begin{keywords}
Policy Modeling; \TODO{Specific Method, e.g., System Dynamics}; Multi-Objective Optimization; Scenario Analysis; Spillover Effects; \TODO{1-2 topic-specific keywords}
\end{keywords}

\end{abstract}
