% Section 9: Conclusions and Recommendations

\section{Conclusions}
\label{sec:conclusion}

\subsection{Summary of Findings}

\begin{enumerate}[itemsep=0.2em]
    \item \textbf{Dual-Core Inversion + Posterior Reconstruction:} LP/MILP yields feasible intervals; truncated Bayesian MCMC produces 2,250 contestant-week posteriors with median HDI width 0.268.
    \item \textbf{Rule Transparency Audit:} Slack indicator $S^*$ remains at 0 across seasons, indicating consistency with published rules under our assumptions.
    \item \textbf{Counterfactual Stability:} Mean Kendall's Tau $\approx 0.455$ and reversal rate $\approx 0.174$ quantify persistent but bounded judge--fan tension.
    \item \textbf{Feature Attribution:} XGBoost + SHAP show judge-score statistics and partner effects dominate survival outcomes.
    \item \textbf{Mechanism Design:} A dynamic adaptive weighting schedule balances fairness and fan influence, with 60/40 as a strong static baseline.
\end{enumerate}

\subsection{Recommendations}

\begin{enumerate}[itemsep=0.2em]
    \item \textbf{Pre-Broadcast Transparency:} Run the inversion audit before broadcast to identify high-uncertainty weeks.
    \item \textbf{Adopt Dynamic Weighting:} Emphasize judges early (skill screening) and shift toward fans late (engagement).
    \item \textbf{Judges' Save Clarity:} Publicly document save criteria to reduce perceived opacity.
\end{enumerate}

\subsection{Limitations}

\begin{itemize}[itemsep=0.1em]
    \item Unobserved shocks (media events, campaign effects) are not modeled.
    \item Rank-only seasons remain weakly identified despite MILP constraints.
    \item Counterfactuals assume fan behavior is invariant to rule changes.
\end{itemize}

\subsection{Future Work}

Future extensions include external popularity priors, adaptive MCMC proposals, and real-time producer dashboards.

\vspace{0.5em}
\noindent\textbf{Key Takeaway:} A rule-consistent Bayesian reconstruction enables fair, explainable audits and motivates a dynamic mechanism that balances skill and popularity.
