% Memo: Executive Brief for DWTS Programming Leadership

\newpage
\thispagestyle{empty}

\begin{center}
\Large\textbf{AUDIT MEMORANDUM}
\end{center}

\vspace{0.5em}
\noindent\rule{\textwidth}{1.5pt}
\vspace{0.3em}

\begin{tabular}{@{}ll}
\textbf{TO:}      & Executive Producer, \emph{Dancing with the Stars} \\
\textbf{FROM:}    & Team \#2617892 --- Modeling \& Audit Unit \\
\textbf{DATE:}    & January 30, 2026 \\
\textbf{SUBJECT:} & \textbf{Transparency Risks \& Rule Recommendations}
\end{tabular}

\vspace{0.3em}
\noindent\rule{\textwidth}{1.5pt}
\vspace{0.8em}

\subsection*{Executive Summary}

We conducted an independent audit of DWTS elimination outcomes across all 34 US seasons. Our analysis addresses a fundamental question: \textbf{Can the show's published scoring rules explain the observed eliminations without ever observing individual fan vote shares?}

For 32 of 34 seasons, the answer is \textbf{yes}---our mathematical model finds feasible fan vote distributions consistent with all outcomes. For \textbf{Seasons 32--33}, however, structural mismatches exist: no feasible vote assignment can fully reproduce the observed eliminations under stated rules.

\subsection*{Key Finding (Audit Perspective)}

Beginning in S28, the Judges' Save introduces a layer of \textbf{decision opacity}: the broadcasted ``bottom-two'' procedure is rule-driven, but the final elimination depends on qualitative criteria not disclosed in a verifiable form. This does not imply wrongdoing; however, it \textbf{raises audit risk} by making certain outcomes \textbf{non-reproducible} under a purely rule-based model.

\subsection*{Three Principal Findings}

\begin{enumerate}[itemsep=0.2em]
    \item \textbf{Model--Data Mismatch in Recent Seasons.} \\
    Seasons 32 and 33 exhibit positive slack ($S^* > 0$) in our optimization framework, indicating outcomes that cannot be explained by feasible vote assignments under documented rules. Likely cause: the Judges' Save criterion operates on undisclosed factors (``improvement,'' ``artistry'') not captured by score-based logic. \textit{Implication: Audit trail is incomplete for these seasons.}
    
    \item \textbf{Structural Vulnerability to Fan-Base Mobilization.} \\
    The current 50/50 judge--fan split allows contestants with mobilized fan bases to survive despite low technical scores. Season 27 (Bobby Bones) exemplifies this: our inferred vote intervals show a contestant can advance with approximately 25--30\% fan support if competitors' votes are fragmented. \textit{Implication: Competitive integrity risk exists under current mechanism.}
    
    \item \textbf{40 Definite-Wrongful Eliminations Identified.} \\
    Using interval-robust classification, we identified 40 historical eliminations where the eliminated contestant had \emph{both} above-median judge scores \emph{and} above-median estimated fan support across all feasible vote assignments. A mechanism adjustment would reduce this to \textbf{3} cases.
\end{enumerate}

\subsection*{Recommendation: Weighted Percent Mechanism}

To improve transparency without sacrificing engagement, we recommend:

\begin{itemize}[itemsep=0.1em]
    \item \textbf{Adopt a 60/40 weighting:} $0.6 \times \text{JudgePct} + 0.4 \times \text{FanPct}$
    \item \textbf{Impact:} Reduces Definite-Wrongful eliminations from 40 to 3 ($-92.5\%$)
    \item \textbf{Robustness:} Performance stable across $\alpha \in [0.55, 0.65]$ (Pareto knee)
    \item \textbf{Fan engagement preserved:} 68\% of historical fan influence retained
\end{itemize}

\noindent Additionally, consider reporting minimal verifiable information (e.g., bottom-two composition) to improve audit trail completeness.

\subsection*{Scope \& Limitations}

\begin{itemize}[itemsep=0.1em]
    \item We never observe actual vote counts---our analysis produces \emph{feasible intervals}, not exact values.
    \item Mismatch events signal \textbf{model--data discrepancy}, not manipulation.
    \item Post-S27 rule details are inferred from problem statement; official documentation may differ.
\end{itemize}

\vspace{0.8em}
\hfill\textbf{--- Team \#2617892, Modeling \& Audit Unit}

\vspace{0.3em}
\hfill\textit{Full technical methodology in attached report.}
