% Appendix: AI Tools Usage Disclosure
% 附录：AI工具使用声明（按COMAP 2026要求）

\section*{AI Report}
\addcontentsline{toc}{section}{AI Report}
\label{appendix:ai}

In accordance with COMAP 2026 rules, we disclose all uses of artificial intelligence (AI) tools during the preparation of this paper.

% AI工具总览
\subsection*{AI Tools Used}
\label{subsec:ai_tools}

\begin{itemize}[itemsep=0.3em]
    \item \textbf{Claude Opus 4.5 (via GitHub Copilot)} -- Code architecture design, algorithm implementation, debugging
    \item \textbf{ChatGPT-4o} -- Language polishing and grammar checking
    \item \textbf{GitHub Copilot} -- Code assistance for Python modules
    \item \textbf{DeepL Translator} -- Technical term translation (Chinese $\leftrightarrow$ English)
\end{itemize}

% 各章节AI使用明细
\subsection*{AI Usage by Section/Task}
\label{subsec:ai_usage}

\begin{table}[H]
    \centering
    \caption{Detailed AI Usage Log}
    \label{tab:ai_disclosure}
    \begin{tabularx}{\textwidth}{l l X}
        \toprule
        \textbf{AI Tool} & \textbf{Section/Task} & \textbf{Specific Usage} \\
        \midrule
        Claude Opus 4.5 & Model Design & Assisted in formulating the LP/CP dual-core inversion framework. Mathematical constraints and algorithm logic designed collaboratively with team. \\
        \addlinespace[0.4em]
        Claude Opus 4.5 & Code Implementation & Generated Python module structure for \texttt{dwts\_model} package including ETL, engines, sampling, analysis, mechanism, and visualization modules. \\
        \addlinespace[0.4em]
        Claude Opus 4.5 & Anomaly Detection & Designed the ``Money Plot'' sensitivity analysis framework for detecting infeasible seasons (S32, S33). \\
        \addlinespace[0.4em]
        Claude Opus 4.5 & Mechanism Design & Developed the Weighted Borda Count mechanism and counterfactual simulation framework. \\
        \addlinespace[0.4em]
        ChatGPT-4o & Abstract \& Intro & Polishing English grammar and improving fluency. All technical content written by team. \\
        \addlinespace[0.4em]
        GitHub Copilot & Code Refinement & Assisted in writing utility functions and test cases. Core algorithmic logic designed by team. \\
        \addlinespace[0.4em]
        DeepL & Throughout & Translated technical terms. All text reviewed and revised by team. \\
        \bottomrule
    \end{tabularx}
\end{table}

% 验证与人工监督
\subsection*{Verification \& Human Oversight}
\label{subsec:verification}

\begin{enumerate}[itemsep=0.4em]
    \item \textbf{Human Review:} All AI-generated content was carefully reviewed, verified, and often substantially modified before inclusion. Key results (92.5\% improvement, S32/S33 anomalies) were independently validated.
    \item \textbf{Code Testing:} All code assisted by AI tools was independently tested on the full DWTS dataset to ensure correctness and reproducibility.
    \item \textbf{Mathematical Verification:} LP/CP formulations were manually derived and cross-checked against optimization theory textbooks.
    \item \textbf{Domain Knowledge:} DWTS rule changes were verified against official production documents and fan archives; AI was not relied upon for factual claims about the show.
\end{enumerate}

% 人类独创内容
\subsection*{Original Human Contributions}
\label{subsec:human_original}

The following elements were created entirely by the human team without AI assistance:

\begin{itemize}[itemsep=0.3em]
    \item Problem formulation and research questions
    \item Data collection and rule verification from official sources
    \item Interpretation of anomaly detection results (why S32/S33 are anomalies)
    \item Policy recommendations in the ``Safety Net Protocol''
    \item Final parameter choices ($\alpha = 0.6$, $\epsilon = 1\%$) based on domain reasoning
\end{itemize}

% 团队声明
\subsection*{Team Statement}
\label{subsec:team_statement}

We affirm that while AI tools significantly accelerated our workflow, all substantive intellectual contributions---problem framing, model design decisions, result interpretation, and policy recommendations---reflect the collective judgment of our human team. The AI tools served as sophisticated assistants, not autonomous decision-makers.

\vspace{1em}
\noindent\textbf{Signed:} Team \#2617892
