% 12_ai_tool_report.tex - AI工具使用报告
% ICM Problem F - AI使用合规声明

\section*{Appendix C: AI Tool Usage Report}
\addcontentsline{toc}{section}{Appendix C: AI Tool Usage Report}
\label{app:ai}

% 【写作指导】MCM/ICM 2025+ 要求披露AI使用情况
% 本附录需要：诚实、具体、可追溯

\subsection*{C.1 AI Tools Employed}

The following AI-powered tools were used during the development of this paper:

\begin{table}[H]
\centering
\caption{AI Tools Usage Summary}
\label{tab:ai_tools}
\small
\begin{tabular}{p{2.5cm} p{2.5cm} p{6cm} p{3cm}}
\toprule
\textbf{Tool Name} & \textbf{Provider} & \textbf{Purpose} & \textbf{Usage Extent} \\
\midrule
\TODO{e.g., ChatGPT-4} & \TODO{OpenAI} & \TODO{e.g., Literature review assistance, equation derivation checking} & \TODO{Moderate} \\
\TODO{e.g., GitHub Copilot} & \TODO{Microsoft} & \TODO{e.g., Code completion and debugging assistance} & \TODO{Light} \\
\TODO{e.g., Grammarly} & \TODO{Grammarly Inc.} & \TODO{e.g., Grammar and style checking for English writing} & \TODO{Heavy} \\
\TODO{Tool 4} & \TODO{Provider} & \TODO{Purpose description} & \TODO{Extent} \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{C.2 Detailed Usage Description}

\textbf{Literature Review \& Background Research}

\TODO{Describe how AI was used for initial literature search, concept clarification, or background understanding. Example: ``We used ChatGPT to generate initial keyword suggestions for literature search and to explain unfamiliar technical concepts in system dynamics modeling.''}

\textbf{Model Development}

\TODO{Describe AI assistance in model formulation. Example: ``GitHub Copilot provided code completion suggestions during Python implementation. All mathematical formulations were independently derived and verified by team members.''}

\textbf{Writing \& Editing}

\TODO{Describe writing assistance. Example: ``Grammarly was used to check grammar and improve clarity of English prose. ChatGPT was occasionally consulted for phrasing suggestions, particularly for translating technical concepts for non-specialist readers.''}

\textbf{Visualization}

\TODO{Describe any AI-assisted figure generation. Example: ``DALL-E was not used. All figures were created manually using matplotlib, TikZ, or standard plotting tools.''}

\subsection*{C.3 Human Oversight Statement}

We affirm that:

\begin{enumerate}
    \item \textbf{Original Thinking:} All core ideas, model formulations, and policy recommendations originated from human team members. AI tools provided support but did not generate novel intellectual contributions.
    
    \item \textbf{Verification:} All AI-generated suggestions (code, text, equations) were critically reviewed and verified by team members before inclusion.
    
    \item \textbf{Accountability:} Team members take full responsibility for the accuracy, integrity, and originality of this work.
    
    \item \textbf{No Fabrication:} No AI tool was used to fabricate data, results, or citations. All references are real and were verified by team members.
\end{enumerate}

\subsection*{C.4 Specific AI Interaction Log}

For transparency, we provide representative examples of AI interactions:

\begin{table}[H]
\centering
\caption{Sample AI Interaction Log}
\label{tab:ai_log}
\small
\begin{tabular}{p{1.5cm} p{2cm} p{4.5cm} p{5.5cm}}
\toprule
\textbf{Date} & \textbf{Tool} & \textbf{Query/Task} & \textbf{Outcome \& Human Follow-up} \\
\midrule
\TODO{Date} & \TODO{Tool} & \TODO{e.g., ``Explain Sobol sensitivity analysis''} & \TODO{e.g., ``Used explanation as starting point; read original Sobol (1993) paper for verification''} \\
\TODO{Date} & \TODO{Tool} & \TODO{Query description} & \TODO{Outcome description} \\
\TODO{Date} & \TODO{Tool} & \TODO{Query description} & \TODO{Outcome description} \\
\bottomrule
\end{tabular}
\end{table}

\noindent\textit{Complete interaction logs are maintained by the team and available upon request for audit purposes.}

\subsection*{C.5 Compliance Statement}

This work complies with the MCM/ICM AI usage guidelines. We have:

\begin{itemize}
    \item[$\checkmark$] Disclosed all AI tools used
    \item[$\checkmark$] Described the nature and extent of AI assistance
    \item[$\checkmark$] Ensured human oversight of all AI-generated content
    \item[$\checkmark$] Verified the accuracy of any AI-assisted outputs
    \item[$\checkmark$] Taken full responsibility for the final work product
\end{itemize}

\vspace{1em}
\begin{center}
\textit{Signed: Team \#2617892}\\
\textit{Date: \today}
\end{center}
