% Section 1: Introduction

\section{Introduction}
\label{sec:intro}

\subsection{Background}

\emph{Dancing with the Stars} (DWTS) has run 34 seasons since 2005, pairing celebrities with professional dancers. Judge scores are public, but \emph{individual fan vote shares are never disclosed}---creating challenges for producers (anomaly detection), advertisers (popularity estimation), and researchers (voting behavior analysis).

\subsection{Problem Statement}

We address five interconnected questions (MCM Problem C Tasks):
\begin{enumerate}[itemsep=0.1em]
    \item \textbf{Fan Vote Inference:} Reconstruct plausible fan vote distributions from eliminations.
    \item \textbf{Rule Change Impact:} How do immunity, double eliminations, and judge saves affect inference?
    \item \textbf{Success Factors:} What predicts survival (profession, partner, fame)?
    \item \textbf{Mechanism Evaluation:} Does the current system produce ``fair'' outcomes?
    \item \textbf{Mechanism Design:} Can we improve fairness while maintaining engagement?
\end{enumerate}

\subsection{Contributions}

\begin{enumerate}[itemsep=0.1em]
    \item \textbf{Dual-Core Engine:} LP (percent seasons) + CP (rank seasons) for fan vote inference.
    \item \textbf{Anomaly Detection:} S32/S33 identified as structurally infeasible.
    \item \textbf{Survival Analysis:} Pro dancer explains 42.9\% of variance.
    \item \textbf{Weighted Borda:} 92.5\% reduction in wrongful eliminations.
    \item \textbf{Safety Net Protocol:} Actionable recommendations for producers.
\end{enumerate}

\subsection{Paper Organization}

\secref{sec:assumptions}: Assumptions; \secref{sec:notations}: Notations; \secref{sec:model1}: Fan Vote Inversion; \secref{sec:model2}: Survival Analysis; \secref{sec:model3}: Mechanism Design; \secref{sec:sensitivity}: Sensitivity; \secref{sec:evaluation}: Evaluation; \secref{sec:conclusion}: Conclusions.
