% Section 2: Assumptions and Justifications
% 假设条件及其合理性说明

\section{Assumptions and Justifications}
\label{sec:assumptions}

To establish a reasonable and solvable mathematical model for the DWTS fan vote inference problem, we make the following assumptions. Each assumption is justified with a brief rationale.

\begin{enumerate}[label=\textbf{H\arabic*.}, leftmargin=2em, itemsep=0.6em]
    
    \item \textbf{Rational Voting Assumption.}
    Viewers cast votes sincerely based on their preferences; strategic voting (e.g., voting for weak competitors to eliminate threats) is negligible.
    
    \textit{Justification:} While strategic voting exists in theory, empirical evidence from fan forums suggests the vast majority of DWTS viewers vote for their favorite contestant rather than tactically~\cite{dwts_voting_analysis}.
    
    \item \textbf{Elimination Truthfulness Assumption.}
    The announced elimination outcomes accurately reflect the application of stated voting rules (judge scores combined with fan votes).
    
    \textit{Justification:} Any systematic deviation would constitute fraud; we model such deviations as \emph{anomalies} to be detected rather than assumed away.
    
    \item \textbf{Vote Share Regularity Assumption.}
    Each contestant receives a non-trivial minimum vote share $\epsilon > 0$ in any week they compete.
    
    \textit{Justification:} Even unpopular contestants have supporters; a zero vote share is implausible given millions of viewers. We treat $\epsilon$ as a sensitivity parameter (default: 1\%).
    
    \item \textbf{Rule Documentation Accuracy.}
    Production rules (immunity windows, double eliminations, judge saves) documented in official sources accurately describe the actual voting mechanics.
    
    \textit{Justification:} We cross-reference multiple sources (Wikipedia, official ABC press releases, fan archives) to verify rule changes. Discrepancies are flagged for manual review.
    
    \item \textbf{Judge Score Independence.}
    Judge scores are determined independently of fan vote information, which is not revealed to judges before scoring.
    
    \textit{Justification:} DWTS production protocol ensures judges score performances before any vote tallying occurs.
    
    \item \textbf{Temporal Independence Within Weeks.}
    Fan voting behavior in week $w$ does not directly depend on unobserved vote shares from week $w-1$ (only on observable outcomes like eliminations and scores).
    
    \textit{Justification:} Since individual vote shares are never published, fans cannot condition their votes on this hidden information. They observe only survival/elimination outcomes.
    
    \item \textbf{External Shock Detectability.}
    Major external shocks (production interventions, voting system failures, scandal-driven viewer mobilization) manifest as constraint infeasibility in our inversion model.
    
    \textit{Justification:} Our anomaly detection framework is designed to flag seasons where standard elimination logic cannot explain outcomes, which we interpret as evidence of external shocks.

\end{enumerate}
