% Memo: Safety Net Protocol Recommendation
% 备忘录：安全网协议建议

\newpage
\thispagestyle{empty}

\begin{center}
\Large\textbf{MEMORANDUM}
\end{center}

\vspace{1em}

\noindent\rule{\textwidth}{1.5pt}

\vspace{0.5em}

\begin{tabular}{@{}ll}
\textbf{TO:}      & Director of Programming, \emph{Dancing with the Stars} \\[0.3em]
\textbf{FROM:}    & Team \#2617892, Senior Data Forensic Consultants \\[0.3em]
\textbf{DATE:}    & January 26, 2026 \\[0.3em]
\textbf{SUBJECT:} & \textbf{URGENT: System Integrity Failure Detected in Season 32}
\end{tabular}

\vspace{0.5em}

\noindent\rule{\textwidth}{1.5pt}

\vspace{1.5em}

%=== Opening ===
\subsection*{Executive Summary}

Our forensic audit of all 34 seasons of \emph{Dancing with the Stars} reveals a critical finding: \textbf{the current ``Judges' Save'' mechanic has mathematically broken the competition's fairness.} Beginning in Season 32, the voting system produces outcomes that are \emph{structurally infeasible}---no combination of fan votes and judge scores can explain the observed eliminations under the published rules.

This is not a minor anomaly. It is a \textbf{System Integrity Failure} that undermines viewer trust and exposes the production to accusations of manipulation.

%=== The Evidence ===
\subsection*{The Evidence: Mathematical Infeasibility}

We developed a Dual-Core Inversion Engine that reconstructs plausible fan vote distributions from elimination outcomes. For 31 consecutive seasons (S1--S31), our model achieved \textbf{100\% feasibility}---every elimination could be explained by the stated rules.

Beginning with \textbf{Season 32}, this changed dramatically. As shown in Figure~\ref{fig:inconsistency} (The Inconsistency Spectrum), the constraint slack $S^*$ spiked from near-zero to $S^* = 2.0$. This means:

\begin{itemize}[itemsep=0.3em]
    \item The ``feasible region'' for fan votes \textbf{collapsed entirely}.
    \item No valid fan vote distribution exists that satisfies the elimination sequence.
    \item The Judges' Save mechanic created outcomes that \textbf{cannot be mathematically justified}.
\end{itemize}

\noindent\textbf{Bottom line:} The published rules say one thing; the results say another. This gap is measurable, significant, and damaging.

%=== The Solution ===
\subsection*{The Solution: Safety Net Protocol}

We propose a two-tier \textbf{Safety Net Protocol} to restore system integrity while preserving viewer engagement:

\vspace{0.5em}

\begin{tcolorbox}[colback=blue!5, colframe=blue!50!black, title=\textbf{Tier 1: Soft Floor (The ``Melting Point'')}]
\textbf{Mechanism:} Contestants with judge scores below the 25th percentile receive a ``protection buffer'' that prevents immediate elimination solely due to low fan votes.

\textbf{Rationale:} This prevents the scenario where a technically skilled dancer is eliminated in early rounds due to lack of name recognition, while still allowing fan preferences to dominate in later rounds.

\textbf{Formula:} If $J_i < Q_{25}(\mathbf{J})$, then $C_i^{\text{eff}} = \max(C_i, \theta_{\text{floor}})$
\end{tcolorbox}

\vspace{0.5em}

\begin{tcolorbox}[colback=green!5, colframe=green!50!black, title=\textbf{Tier 2: Dynamic Mix (Rank/Percent Hybrid)}]
\textbf{Mechanism:} Replace the current 50/50 additive system with a \textbf{Weighted Borda Count}:
\[
\text{Score}_i = 0.6 \times \widetilde{J}_i + 0.4 \times \widetilde{V}_i
\]
where $\widetilde{J}_i$ and $\widetilde{V}_i$ are min-max normalized scores.

\textbf{Rationale:} Our counterfactual simulations show this reduces ``wrongful eliminations'' by \textbf{92.5\%} (from 40 cases to 3 cases across 230 elimination rounds).

\textbf{Benefit:} Simple, transparent, and easily communicated to viewers as ``60\% skill, 40\% fan support.''
\end{tcolorbox}

\vspace{0.5em}

\begin{tcolorbox}[colback=yellow!5, colframe=orange!50!black, title=\textbf{Pre-Broadcast Feasibility Check}]
\textbf{Implementation:} Before each live results show, run our LP/CP solver on the current week's data. If the constraint system reports $S^* > 0.5$, \textbf{flag the episode for manual review} before announcing results.

\textbf{Runtime:} $< 5$ seconds on standard hardware.

\textbf{Impact:} Would have detected the S32 and S33 anomalies \emph{before} public broadcast, enabling investigation of potential voting irregularities, undisclosed rule modifications, or data entry errors.
\end{tcolorbox}

%=== Closing ===
\subsection*{Recommendation}

Adopting this protocol restores the \textbf{``Professional Floor''}---ensuring technical excellence is rewarded---while keeping the \textbf{``Popular Ceiling''}---maintaining the viewer engagement that drives ratings and advertising revenue.

The math is clear. The solution is ready. \textbf{We advise immediate implementation for Season 35.}

\vspace{1.5em}

\noindent\rule{\textwidth}{0.5pt}

\vspace{0.5em}

\noindent\textit{This memo accompanies our full technical report. For detailed methodology, proofs, and sensitivity analyses, please refer to Sections 4--7 of the attached paper.}

\vspace{1em}

\hfill\textbf{--- Team \#2617892}
