% Appendix: AI Tools Usage Disclosure
% 附录：AI工具使用声明（按COMAP 2026要求）

\section*{AI Report}
\addcontentsline{toc}{section}{AI Report}
\label{appendix:ai}

In accordance with COMAP 2026 rules, we provide a complete and transparent disclosure of all artificial intelligence (AI) tools used during the preparation of this paper.

%=== AI工具总览 ===
\subsection*{AI Tools Used}
\label{subsec:ai_tools}

The following AI tools were employed as auxiliary aids during this project:

\begin{itemize}[itemsep=0.3em]
    \item \textbf{ChatGPT-4o / GPT-4} -- Language polishing, grammar checking, and clarity improvement
    \item \textbf{GitHub Copilot} -- Code assistance for data preprocessing and visualization scripts
    \item \textbf{Claude 3.5 Sonnet} -- LaTeX formatting, structural organization, and notation consistency
    \item \textbf{DeepL Translator} -- Technical term translation (Chinese $\leftrightarrow$ English)
    \item \textbf{Grammarly} -- Proofreading and style consistency
\end{itemize}

%=== 各章节AI使用明细 ===
\subsection*{AI Usage by Section/Task}
\label{subsec:ai_usage}

\begin{table}[H]
    \centering
    \caption{Detailed AI Usage Log}
    \label{tab:ai_disclosure}
    \begin{tabularx}{\textwidth}{l l X}
        \toprule
        \textbf{AI Tool} & \textbf{Section/Task} & \textbf{Specific Usage and Human Oversight} \\
        \midrule
        ChatGPT-4o & Abstract, Intro & 
        Polished English grammar and improved sentence fluency. All technical content, problem analysis, and framing written by team members. \\
        \addlinespace[0.5em]
        
        GitHub Copilot & Code (Appendix) & 
        Assisted in writing Python scripts for data preprocessing, System Dynamics simulation, and TOPSIS calculation. All algorithmic logic, model design, and parameter choices determined by team. \\
        \addlinespace[0.5em]
        
        Claude 3.5 Sonnet & Model Sections & 
        Helped organize mathematical notations, check LaTeX syntax, and format equations. All mathematical derivations and model formulations are original work. \\
        \addlinespace[0.5em]
        
        DeepL & Throughout & 
        Translated technical terminology between Chinese and English. All translations reviewed and verified by bilingual team members. \\
        \addlinespace[0.5em]
        
        Grammarly & Final Draft & 
        Proofreading for typos and grammar errors. All substantive edits made by human authors. \\
        \bottomrule
    \end{tabularx}
\end{table}

%=== AI使用边界声明 ===
\subsection*{AI Usage Boundaries}
\label{subsec:ai_boundaries}

We explicitly state that AI tools were \textbf{NOT} used for:

\begin{enumerate}[itemsep=0.3em]
    \item \textbf{Problem Analysis and Interpretation:} Understanding and reframing the ICM Problem E requirements was conducted entirely by human team members.
    
    \item \textbf{Modeling Decisions:} Selection of System Dynamics methodology, sustainability indicator framework, MCDA approach, and scenario design were human decisions based on literature review and domain knowledge.
    
    \item \textbf{Assumption Formulation:} All model assumptions and their justifications reflect human judgment about the problem context.
    
    \item \textbf{Data Analysis and Interpretation:} Analysis of simulation results, identification of patterns, and drawing conclusions were performed by team members.
    
    \item \textbf{Policy Recommendations:} All policy recommendations are the intellectual product of human deliberation, drawing on the quantitative analysis.
    
    \item \textbf{Critical Evaluation:} Assessment of model strengths, weaknesses, and limitations reflects genuine self-critique by the team.
\end{enumerate}

%=== 验证与人工监督 ===
\subsection*{Verification and Human Oversight}
\label{subsec:verification}

\begin{enumerate}[itemsep=0.4em]
    \item \textbf{Human Review:} All AI-assisted content was carefully reviewed, verified, and substantially modified before inclusion. AI suggestions were treated as drafts, not final outputs.
    
    \item \textbf{Code Testing:} All code, whether assisted by AI or not, was independently tested and validated to ensure correctness, reproducibility, and alignment with intended logic.
    
    \item \textbf{Mathematical Verification:} All equations, derivations, and calculations were manually verified by team members with relevant mathematical background.
    
    \item \textbf{Consistency Checking:} Cross-references, notation consistency, and logical flow were manually checked across all sections.
    
    \item \textbf{Originality Verification:} Key passages were checked to ensure no inadvertent reproduction of copyrighted material.
\end{enumerate}

%=== 原创性声明 ===
\subsection*{Originality and Responsibility Statement}
\label{subsec:originality}

We, Team \#2617892, hereby declare:

\begin{enumerate}[itemsep=0.4em]
    \item \textbf{Core Intellectual Work:} All problem analysis, mathematical modeling, algorithm design, data interpretation, and innovative contributions in this paper are the \textbf{original work} of our team.
    
    \item \textbf{AI as Auxiliary Tool Only:} AI tools were used solely as auxiliary aids for language quality, formatting, and repetitive coding tasks. \textbf{No AI was used to generate core modeling ideas, derive conclusions, or make policy recommendations.}
    
    \item \textbf{Full Responsibility:} We take full responsibility for all content in this paper, including any errors or omissions. AI tools do not share authorship or accountability.
    
    \item \textbf{Academic Integrity:} We have read and understood COMAP 2026 rules regarding AI usage. This disclosure is complete, accurate, and made in good faith.
\end{enumerate}

\vspace{1.5cm}
\noindent\rule{\textwidth}{0.4pt}

\noindent
\textbf{Team \#2617892}\\
\noindent Date: \today

\vspace{0.5cm}
\noindent
\textit{This AI usage report is submitted in compliance with COMAP MCM/ICM 2026 competition rules and reflects our commitment to transparency and academic integrity.}
